---
title: "Arizona-Pesticide-Usage-Map"
author: "LT, MF"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: menu
    source_code: embed
    # https://github.com/walkerke/neighborhood_diversity
    theme: cerulean
---

```{r gloval, include=FALSE}
pacman::p_load(flexdashboard, shiny, leaflet, leafpop, leafem, mapview, dplyr, ggplot2, plotly, scales)

counties <- c("APACHE", "COCHISE","COCONINO", "GILA", "GRAHAM", "GREENLEE", "LA PAZ",
                        "MARICOPA", "MOHAVE", "NAVAJO", "PIMA","PINAL", "SANTA CRUZ", "YAVAPAI",
                        "YUMA")

ingredients <- c("BENSULIDE", "CHLORPYRIFOS",
                        "METHOMYL", "ACEPHATE","DIMETHOATE","MALATHION",
                        "PERMETHRIN","LAMBDA-CYHALOTHRIN", "ZETA-CYPERMETHRIN","DIAZINON",
                        "BIFENTHRIN","CARBARYL","METHYL PARATHION","ESFENVALERATE",
                        "TRIBUFOS", "ALDICARB", "OXAMYL", "FENPROPATHRIN", "ETHEPHON",
                        "BETA-CYFLUTHRIN")


# Read in data, and subset for the selected county
data <- readRDS(file = "./data/cleaned_pesticides.rds")
year <- read.csv(file ="./data/total_yearly.csv")
month <- read.csv(file ="./data/total_monthly.csv")

dat <- reactive({

  data %>% dplyr::filter(County == input$county & year == input$year & Active.Ingredient.new ==input$ingredient)
  
})

yearly <- reactive({

  year %>% dplyr::filter(County == input$county)
  
})

monthly <- reactive({

 month %>% dplyr::filter(County == input$county & year == input$year & Active.Ingredient.new ==input$ingredient)
  
})


# test
# p <- month %>% dplyr::filter(County == "YUMA" & year == 2006 & Active.Ingredient.new == "CHLORPYRIFOS") %>%
#     mutate(text = glue::glue("Month: {month}<br>Total: {round(total, 2)}")) %>%
#     ggplot(aes(month %>% as.factor(), total)) +
#                         geom_point() +
#                         geom_line(group=0) +
#                         xlab("Month") + ylab("Total pesticide usage (lbs)") +
#                         + theme_bw(axis.text.x = element_text(angle = 45))
# 
# ggplotly(p, source = 'source', tooltip = "text") %>%
#     layout(dragmode = 'lasso',
#            yaxis = list(title = 'Total pesticide usage (lbs)'),
#            margin = list(l = 100),
#            font = list(family = 'Open Sans', size = 16))
# dat <- data  %>% dplyr::filter(County == "YUMA" & year == 2006 & Active.Ingredient.new == "CHLORPYRIFOS")
# mapview(dat,
#           crs = 4269,
#           grid = FALSE,
#           zcol = "AI_amount",
#           popup = popupTable(dat, zcol = c("year",
#                                               "County",
#                                               "Crop.Name",
#                                               "Active.Ingredient.new",
#                                               "AI_amount")))
```


Sidebar {.sidebar}
======================================================================

```{r}
tags$br()
# Define inputs
# select county
selectInput(
            inputId = "county",
            label = "Explore county",
            choices = counties,
            selected = "YUMA",
            multiple = FALSE)
                                      
# select ingredient
selectInput(
            inputId = "ingredient",
            label = "Select an ingredient",
            choices = ingredients,
            selected = "CHLORPYRIFOS",
            multiple = FALSE)
                                      
# Year
# select mode
selectInput(
            inputId = "year",
            label = "Explore year",
            choices = 1992:2016,
            selected = 2006,
            multiple = FALSE)
                                      

```

Use the __Explore county__ tab to explore yearly and month pesticide usage for your chosen AZ county in 2020.  The map presents the selected pesticide usage in targeted county in a selected year, across our sampling sites in AZ. To learn more about the project, click the __About__ tab.  

Author: [Tuo Liu](https://tuo-liu.netlify.app), [Melissa Furlong](https://live-azs-furlonglab.pantheonsite.io)

Data sources: [AZARG](https://live-azs-furlonglab.pantheonsite.io), Arizona ARG

Explore county
======================================================================

Row {data-height=600}
----------------------------------------------------------------------

### Pesticide use by geo-code

```{r}
output$map <- renderLeaflet({
  d <- dat() 
 
  m <- mapview(d,
          crs = 4269,
          grid = FALSE,
          zcol = "AI_amount",
          popup = popupTable(d, zcol = c("year","County","Crop.Name",
                                           "Active.Ingredient.new","AI_amount")))
  m@map
})

leafletOutput('map')
```


Row
-------------------------------------

### Yearly pesticide usage
```{r}
# Here, we draw the yearly usage scatter plot with ggplotly
output$scatter1 <- renderPlotly({
  m1 <- yearly() %>% mutate(
  text = glue::glue("Year: {year}<br>Total: {round(total, 2)}"))


  p1 <- ggplot(m1, aes(year %>% as.factor(), total, text=text)) +
                        geom_point() +
                        geom_line(group=0) +
                        xlab("Year") + 
                        theme(axis.text.x = element_text(angle = 45))
    

   plotly::ggplotly(p1, source = 'source', tooltip = "text") %>%
   layout(dragmode = 'lasso',
   yaxis = list(title = 'Total yearly usage (lbs)'),
   font = list(size = 16))
})

plotlyOutput('scatter1')
```

### Monthly pesticide usage 
```{r}
# Here, we draw the monthly usage scatter plot with ggplotly
output$scatter2 <- renderPlotly({

  m2 <- monthly() %>%
    mutate(text = glue::glue(
      "Month: {month}<br>Total: {round(total, 2)}"
    )) %>% 
    ggplot(aes(month %>% as.factor(), total, text=text)) +
            geom_point() +
            geom_line(group=0) +
            xlab("Month") + 
            theme(axis.text.x = element_text(angle = 45))

  ggplotly(m2, source = 'source', tooltip = "text") %>%
    layout(dragmode = 'lasso',
           yaxis = list(title = 'Total monthly usage (lbs)'),
           font = list(size = 16)) 

})

plotlyOutput('scatter2')
```



About
============================================================================

Welcome to the Pesticide Use Registry map for Arizona. These data were derived from state records from the Arizona Department of Agriculture, although this mapping and data visualization project is not a product of the Arizona Department of Agriculture. We are researchers at the University of Arizona who are interested in providing information to Arizonans on pesticide use in communities.

This application is in support of the _Pesticide and ADHD study_, ["Prenatal Exposure to Pesticide Mixtures and Childhood ADHD"](https://publichealth.arizona.edu/research-project/prenatal-exposure-pesticide-mixtures-and-childhood-adhd). This environmental epidemiology project is a mentored research award (K99/R00) from the National Institute of Environmental Health Sciences (NIEHS). The project's goals are to 
1) create models of atmospheric dispersions of agricultural organophosphorus and pyrethroid pesticide applications over a 20 year period in Arizona, 
2) to construct a case control study of ADHD in Arizona by applying a validated algorithm to Medicaid (AHCCCS) claim records, and 
3) to examine associations between the modeled ambient pesticide concentrations during fetal/early life and ADHD. 

The project also employs the use of novel mixture methods, primarily Bayesian Kernel Machine Regression, to assess the potential for mixture effects of different pesticide exposures.

<!-- The key metric in this article is the neighborhood-level _entropy index_ (called "diversity score" in the application), which measures the degree of neighborhood diversity for six general racial/ethnic groups: non-Hispanic white, non-Hispanic black, Hispanic, Asian/Pacific Islander, Native American.  The entropy index $E$ is calculated as follows (Farrell and Lee 2011):   -->

About the data: The state of Arizona requires that all commercial agricultural pesticide applications, including all aerial applications, be reported to the state. In addition, growers and applicators must report all soil-applied applications of pesticides on the Arizona Department of Environmental Quality’s ground water protection list, and certain odiforous compounds.  Arizona’s Pesticide Use Registry, managed by the Arizona Department of Agriculture, reports information on active ingredient, acres, pounds applied, concentration, Public Land Survey Section (PLSS, location), and application method. The PLSS grid corresponds to approximately a 1 square mile resolution. To enhance this resolution, we linked reported pesticide applications to fields by linking the reported crop target on the PUR with crops from the United States Department of Agriculture’s CropScape rasters, a satellite-based rendering of crop identification, following methods previously used for the California PUR(60-62). We matched targeted crops for the relevant chemical on the pesticide use report, to the satellite-identified crop fields on the CropScape rasters, by year.

Here, we report organophosphate, pyrethroid, and carbamate pesticide applications in the state of Arizona for the years 2006-2016.

The application is built with the [Shiny](http://shiny.rstudio.com) framework for the [R programming language](https://www.r-project.org/). The application layout is produced with the [flexdashboard](http://rstudio.github.io/flexdashboard/index.html) package, and the charts and maps use [Plotly](http://plot.ly), [Leaflet.js](http://leafletjs.com/), and [ggplot2](http://ggplot2.org/), all accessed through their corresponding R packages.  Code for the application is available at [Github](https://github.com/TuoooLiu666/Arizona-Pesticide-Usage-Map).  

To learn more about my work, [visit my website](https://tuoooliu666.github.io/) or [connect with me on LinkedIn](https://www.linkedin.com/in/tuo-l-491782194/).  
 

